### 2019-04-30 papers/haskell19/1-intro.tex
Section 3
Added contributions

>>>>

The main contribution of this paper are:
%
\begin{itemize}
\item We identify some of the most important limitations of performing random
  testing with automatically derived generators using state-of-the-art tools
  (Section \ref{sec:sources}).
\item We present an extensible mechanism for representing random values built
  upon different source constructions using the Data Types \`a la Carte approach
  (Section \ref{sec:representation}).
\item We develop a modular generation schema, exploiting the extensible nature
  of our representations, which are extended to encode information relevant to
  the generation process at the type level (Section \ref{sec:generation}).
\item We present a very simple yet powerful domain specific language for
  describing extensible generators solely based on the types we used to
  represent the desired shape of our random data (Section \ref{sec:type-level}).
\item We provide a Template Haskell tool for automatically deriving all the
  required machinery presented throughout this paper, and evaluate its
  generation performance using three real-world case studies (Section
  \ref{sec:casestudies}).
\end{itemize}

Overall, we present a novel technique for reusing automatically derived
generators in a composable fashion, in contrast with the usual paradigm of
automatically deriving ``closed'' monolithic generators.
